Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-30 automatica/paper.tex
updated description related to the number of benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Our benchmark suite consists of 18 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $167$ different benchmarks
to evaluate our proposal approach.

>>>>

Our benchmark suite consists of 27 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $191$ different benchmarks
to evaluate our proposal approach.
